%% Write your acknowledgements in this file. If you do not want to acknowledge anyone,
%% you can delete this file and comment out the corresponding part in the "thesis.tex"
%% file.
%
I would like to acknowledge the effort put into this thesis by
myself. This work could not have been done without me.


BOVY: SOLAR SYSTEM ACK: First of all we would like to thank Scott
Tremaine for many inspiring discussions that helped shape this
paper. It is also a pleasure to thank Kyle Cranmer, Dustin Lang, Yuri
Levin, Phil Marshall, Bill Press, and Hans-Walter Rix for very helpful
discussions and the anonymous referee for valuable comments. This
research was partially supported by NASA (ADP grant NNX08AJ48G), the
NSF (grant AST-0908357), and a Research Fellowship of the Alexander
von Humboldt Foundation. This project made use of the HORIZONS System
provided by the Solar System Dynamics Group of the Jet Propulsion
Laboratory, the NASA Astrophysics Data System, and the open-source
Python modules scipy, numpy, and matplotlib.

BOVY: MASERS ACK: It is a pleasure to thank Dustin Lang, Mark Reid,
and Scott Tremaine for helpful discussions and the anonymous referee
for valuable comments. JB and DWH were partially supported by NASA
(grant NNX08AJ48G). JB was partially supported by New York
University's Horizon fellowship. DWH is a research fellow of the
Alexander von Humboldt Foundation of Germany. JB was partially
supported by the Max-Planck-Institut f\"ur Astronomie, and is grateful
for its hospitality during part of the period during which this
research was performed. JB also gratefully acknowledges the
hospitality of the Lorentz Center (Leiden) where parts of this
research were performed.

BOVY: MOVING GROUPS I ACK: It is a pleasure to thank Fr{\'e}d{\'e}ric
Arenou, Michael Blanton, Anthony Brown, Walter Dehnen, Kathryn
Johnston, Dustin Lang, Floor van Leeuwen, Hans-Walter Rix, and Scott
Tremaine for comments and assistance. We also thank Walter Dehnen and
James Binney for use of their kinematically unbiased sample. JB and
DWH were partially supported by NASA (grant NNX08AJ48G). During part
of the period in which this research was performed, DWH was a research
fellow of the Alexander von Humboldt Foundation of Germany.


BOVY: HERCULES ACK: It is a pleasure to thank the anonymous referee
for valuable comments and Mike Blanton and David W.~Hogg for helpful
discussions and assistance.  Financial support for this project was
provided by the National Aeronautics and Space Administration (grant
NNX08AJ48G) and the National Science Foundation (grant AST-0908357).



