This dissertation has addressed several of the questions concerning
our Galaxy raised in the introduction. We have shown that the
dynamical inference problem of finding the Galaxy's gravitational
potential, and thus its density profile, from observational kinematic
data is possible in \chaptername s~\ref{chap:solarsystem}
and \ref{chap:masers}. Compared to the full \Gaia\ data set of 10$^9$
objects, the problems considered in these chapters are much smaller (8
planets in \chaptername~\ref{chap:solarsystem}; 18 masers
in \chaptername~\ref{chap:masers}). It will take considerable effort
to adapt the method introduced in \chaptername~\ref{chap:solarsystem}
to much larger data sets without making more assumptions about the
orbital distribution of the tracer set. An additional problem that
will crop up when analyzing the full \Gaia\ data set are that there
will be significant contaminating populations, such as streams of
stars that are in the process of being accreted by the Milky
Way. Since these contaminants do not constitute a relaxed,
steady-state population, they have the potential of biasing the
dynamical inference, and the data analysis methods employed will need
to to deal with these contaminants. We note, however, that such
streams could be very informative about the Galactic potential in
themselves (BOVY: CITE KOPOSOV).

Intermediate-scale problems exist that might bridge the gap between
the small, and contamination-free, data sets used in this dissertation
and the full \Gaia\ data set. These are, for example, the nuclear star
cluster in the Milky Way, where kinematic data is available for
thousands of stars within the central 10 pc (BOVY: CHECK; CITE
ECKART?) that can be used to infer the gravitational potential near
the Milky Way's central black hole, detailed kinematic data on
globular clusters that can be used to infer the clusters mass profile,
including the contribution from an intermediate-mass black hole (BOVY:
CITE ANDERSON), and the local Solar neighborhood, where a wealth of
data exists that can be used to infer the local vertical---\ie,
perpendicular to the plane of the disk---potential. The first two of
these problems are qualitatively similar to the inference problem
considered in \chaptername~\ref{chap:solarsystem} in that these
systems are roughly spherically symmetric and almost certainly
relaxed. The vertical-potential problem is a nice test problem
for \Gaia\ in that it will have similar contamination of non-relaxed
populations as \Gaia; \Gaia\ will in fact be able to perform almost
exactly the same measurement at other locations in the Galaxy, which
will help to pin down the disk's surface-mass density profile and,
thus, the contribution of the dark halo to the inner Milky Way
potential.

We have ignored additional information for the dynamical inference
that comes from elemental abundance information. \Gaia\ will not
obtain detailed elemental abundances, so these data will be sparse
comparaed to the full \Gaia\ data set. Nevertheless, sparse elemental
abundance data for a small set of tracers could be very informative
because it will help in separating different components of the Galaxy,
for example, to separate non-relaxed contaminating populations from
the relaxed population used in the inference. 


We have learned several facts about the evolution of the disk. By
studying the local velocity distribution
(\chaptername~\ref{chap:veldist}) we were able to constrain the
non-axisymmetric structures in the Galaxy convolved with the chemical
evolution of the disk (\chaptername~\ref{chap:groups}). We showed that
there must be a transient component to the Galactic bar and spiral
structure to explain the observations of the local
kinematics. However, the absence of global data for the Milky Way's
disk and the absence of more detailed elemental abundance data means
that these constraints are weak and qualitative at best. As described
in the Introduction, \apogee\ will survey the disk globally with
detailed elemental abundance data for $\approx 100,000$ giant stars
(starting in May 2011). These data will allow the non-axisymmetric
components of the disk to be constrained in detail. We have shown for
one particular scenario---the bar-origin model of the Hercules moving
group---how \apogee, or a similar survey, could test this hypothesis
outside of the immediate Solar neighborhood and constrain the Galactic
bar. Similar predictions will be made for other scenarios such that
they can be tested using \apogee. These predictions can be purely
kinematic, but in combination with chemical evolution models, they can
also specify the distributions of elemental abundances across the
disk. In the end a full chemo-dynamical model of the Galactic disk
should be constructed and tested against the \apogee\ data.

One thing that has been missing from this dissertation is the
interstellar medium; except for the masers we have focused mostly on
non-collisional tracers. The gaseous disk of the Milky Way only
contributes about 10\,percent of the disk's mass and is therefore not
that dynamically relevant. Nevertheless, the gas in the disk does play
an important dynamical role in some important cases: the reservoir of
cold gas from which stars form is the engine that keeps spiral
structure running in galactic disks (without the gas the spirals would
dissolve themselves through spiral heating; BOVY: CITE CARLBERG);
because gas has to orbit on non-intersecting orbits to avoid shocks,
the absence of strong shocks is a constraints on the orbital space and
thus on the potential, which needs to allow non-intersecting
orbits. For dynamical inference gas can also be very informative:
because it prefers more circular orbits, measuring the kinematics of
the gas gives a direct measurement of the Milky Way's circular
velocity at different radii; like stars, gas can pile up at orbital
resonances of the bar and thus be used to constrain the bar. Even
though upcoming surveys are focusing on stellar tracers, further
investigations of the dynamical role of the interstellar medium are
warranted.
